Run the model

### 2022-05-31 scripts/3_model/2_run_model.Rmd
Updating model runs for dissertation

# Clean the environment
rm(list = ls())
```

@@

@@

```{r}
DF_1_no_trading <- DF_results_no_trading %>%
  filter(Country == "KIR") %>%
  left_join(Benchmark_results, by = "Country") %>%
  mutate(
    cost = b_vdsrevenue - VDSrevenue,
    rel_cost = cost / b_vdsrevenue,
    cost_pna_not_kir = VDSrevenue_notKIR - b_vdsrevenue_notKIR,
    rel_cost_pna_not_kir = cost_pna_not_kir / b_vdsrevenue_notKIR,
    cost_all = VDSrevenue_all - b_vdsrevenue_all,
    rel_cost_all = cost_all / b_vdsrevenue_all
  )
```

@@

```{r}
DF_results_with_trading <-
  expand.grid(R = Rvec, theta = thetavec) %>%
  mutate(
    res = map2(
      theta,
      R,
      PNA_with_trading,
      fvec = fvec,
      r = r,
      K = K,
      p = p,
      q = q,
      Xvec = Xvec,
      beta = beta,
      c = c,
      E = E
    )
  ) %>%
  unnest()
```

@@

```{r}
DF_1_with_trading <- DF_results_with_trading %>%
  filter(Country == "KIR") %>%
  left_join(Benchmark_results, by = "Country") %>%
  mutate(
    vessel_days_sold = b_vessel_days - Vessel_Days,
    sales_revenue = vessel_days_sold * VDSprice,
    all_VDSrevenue = VDSrevenue + sales_revenue,
    cost = b_vdsrevenue - all_VDSrevenue,
    rel_cost = cost / b_vdsrevenue,
    cost_pna_not_kir = VDSrevenue_notKIR - b_vdsrevenue_notKIR - sales_revenue,
    rel_cost_pna_not_kir = cost_pna_not_kir / b_vdsrevenue_notKIR,
    cost_all = VDSrevenue_all - b_vdsrevenue_all,
    rel_cost_all = cost_all / b_vdsrevenue_all
  )
```

@@

alphas <- c(0, 0.5, 1)

delta <- 1 / 1.1

@@

>>>>

```

@@

```{r}
no_trade_bm <- DF_results_no_trading %>% 
  filter(R == 0, theta == 0) %>%
  select(
    Country,
    b_harvest = Harvest,
    b_vessel_days = Vessel_Days,
    b_stock = Stock,
    b_stock_i = Stock_i,
    b_vdsprice = VDSprice,
    b_vdsrevenue = VDSrevenue,
    b_vdsrevenue_all = VDSrevenue_all,
    b_vdsrevenue_notKIR = VDSrevenue_notKIR
  )
```

@@

```{r}
DF_1_no_trading <- DF_results_no_trading %>%
  filter(Country == "KIR") %>%
  left_join(no_trade_bm, by = "Country") %>%
  mutate(
    cost = b_vdsrevenue - VDSrevenue,
    rel_cost = cost / b_vdsrevenue,
    cost_pna_not_kir = VDSrevenue_notKIR - b_vdsrevenue_notKIR,
    rel_cost_pna_not_kir = cost_pna_not_kir / b_vdsrevenue_notKIR,
    cost_all = VDSrevenue_all - b_vdsrevenue_all,
    rel_cost_all = cost_all / b_vdsrevenue_all
  )
```

@@

```{r}
DF_results_with_trading <-
  expand.grid(R = Rvec, theta = thetavec) %>%
  mutate(
    res = map2(
      theta,
      R,
      PNA_with_trading,
      fvec = fvec,
      r = r,
      K = K,
      p = p,
      q = q,
      Xvec = Xvec,
      beta = beta,
      c = c,
      E = sum(Evec[1:9])
    )
  ) %>%
  unnest()
```

```{r}
trading_bm <- DF_results_with_trading %>% 
  filter(R == 0, theta == 0) %>%
  select(
    Country,
    b_harvest = Harvest,
    b_vessel_days = Vessel_Days,
    b_stock = Stock,
    b_stock_i = Stock_i,
    b_vdsprice = VDSprice,
    b_vdsrevenue = VDSrevenue,
    b_vdsrevenue_all = VDSrevenue_all,
    b_vdsrevenue_notKIR = VDSrevenue_notKIR
  )
```

@@

```{r}
DF_1_with_trading <- DF_results_with_trading %>%
  filter(Country == "KIR") %>%
  left_join(trading_bm, by = "Country") %>%
  mutate(
    vessel_days_sold = b_vessel_days - Vessel_Days,
    sales_revenue = vessel_days_sold * VDSprice,
    all_VDSrevenue = VDSrevenue + sales_revenue,
    cost = b_vdsrevenue - all_VDSrevenue,
    rel_cost = cost / b_vdsrevenue,
    cost_pna_not_kir = VDSrevenue_notKIR - b_vdsrevenue_notKIR - sales_revenue,
    rel_cost_pna_not_kir = cost_pna_not_kir / b_vdsrevenue_notKIR,
    cost_all = VDSrevenue_all - b_vdsrevenue_all,
    rel_cost_all = cost_all / b_vdsrevenue_all
  )
```

@@

alphas <- c(0, 0.5, 1)
delta <- 1 / 1.1

@@

# Numbers for main text

```{r}
# revenues increase between 0\% and 7\% each
DF_1_no_trading %>% pull(rel_cost_pna_not_kir) %>% range() * 100

# When trading between countries occurs, 88.5\% to 99.2\% of revenue losses can be avoided.
both %>% pull(rel_delta_cost) %>% range() * 100

# implementing a reserve results in long-term losses to the conserving country of 20\% to 93\%, depending on the size of reserve and stock movement
allocation %>%
    filter(R > 0,
           trade) %>% 
    filter(alpha == 1) %>% 
    mutate(trade = ifelse(trade, "Trading", "No Trading"),
           alpha = as.character(alpha)) %>% 
    group_by(trade, alpha, R, theta) %>%
    summarize(rev = sum(rev_tot)) %>%
    ungroup() %>% 
    mutate(cost = (best_rev - rev) / best_rev) %>%
    pull(cost) %>% 
    range() * 100

#However, a biomass-only allocation rule (\emph{i.e.} $\alpha = 0$) results in revenue losses of up to 0.7\%, essentially eliminating the costs of conservation.
allocation %>%
    filter(R > 0,
           trade) %>% 
    filter(alpha == 0) %>% 
    mutate(trade = ifelse(trade, "Trading", "No Trading"),
           alpha = as.character(alpha)) %>% 
    group_by(trade, alpha, R, theta) %>%
    summarize(rev = sum(rev_tot)) %>%
    ungroup() %>% 
    mutate(cost = (best_rev - rev) / best_rev) %>%
    pull(cost) %>% 
    range() * 100
```
